Flabby and injective objects in toposes

### 2022-01-09 paper-flabby-objects.tex
Functionally flabby sets (WIP)

\newcommand{\xra}[1]{\xrightarrow{#1}}
\newcommand{\XXX}[1]{\textbf{\textcolor{red}{XXX: #1}}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\bbb}{\mathfrak{b}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\renewcommand{\P}{\mathcal{P}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\op}{\mathrm{op}}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Mod}{Mod}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\PSh}{PSh}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\renewcommand{\_}{\mathpunct{.}\,}
\newcommand{\effective}{ef{}fective\xspace}

@@

>>>>

\newcommand{\xra}[1]{\xrightarrow{#1}}
\newcommand{\XXX}[1]{\textbf{\textcolor{red}{XXX: #1}}}
\newcommand{\aaa}{\mathfrak{a}}
\newcommand{\bbb}{\mathfrak{b}}
\newcommand{\mmm}{\mathfrak{m}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\E}{\mathcal{E}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\renewcommand{\P}{\mathcal{P}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\defeq}{\vcentcolon=}
\newcommand{\defeqv}{\vcentcolon\equiv}
\newcommand{\op}{\mathrm{op}}
\DeclareMathOperator{\Spec}{Spec}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\Mod}{Mod}
\DeclareMathOperator{\Sh}{Sh}
\DeclareMathOperator{\PSh}{PSh}
\newcommand{\Set}{\mathrm{Set}}
\newcommand{\Eff}{\mathrm{Ef{}f}}
\renewcommand{\_}{\mathpunct{.}\,}
\newcommand{\effective}{ef{}fective\xspace}

@@

\XXX{proper exposition}

\begin{defn}\label{defn:functionally-flabby}
A set~$X$ is \emph{functionally flabby} if and only if there is a
map~$\varepsilon : \P_{\leq1}(X) \to X$ such that for all~$K \in
\P_{\leq1}(X)$, $K \subseteq \{ \varepsilon(K) \}$.\end{defn}

A map~$\varepsilon : \P_{\leq1}(X) \to X$ satisfies the condition in
Definition~\ref{defn:functionally-flabby} if and only if it is a retraction of
the canonical injection~$X \to \P_{\leq1}(X)$.

\begin{prop}For a set~$X$, the following conditions are equivalent:
\begin{enumerate}
\item $X$ is injective.
\item $X$ is functionally flabby.
\end{enumerate}
\end{prop}

\begin{proof}Let~$X$ be an injective set. Then the identity~$X \to X$ can be extended
along the canonical inclusion~$X \to \P_{\leq1}(X)$ to a map~$\varepsilon :
\P_{\leq1}(X) \to X$. This map witnesses that~$X$ is functionally flabby.

Conversely, let~$X$ be a functionally flabby set with witness~$\varepsilon :
\P_{\leq1}(X) \to X$. Let~$i : A \to B$ be an injection and let~$f : A \to X$
be a map. Then~$x \mapsto \varepsilon(f[i^{-1}[\{x\}])$ is an extension of~$f$
along~$i$.
\end{proof}

\begin{prop}Every module embeds canonically into a functionally flabby module.\end{prop}

\begin{proof}Let~$M$ be a module. First we'll assume that~$M$
is a sheaf for some modal operator~$\nabla$ such that for any
formula~$\varphi$, $\nabla(\varphi \vee (\varphi \Rightarrow \nabla\bot))$. In
this case, the module~$M$ is already functionally flabby: A witnessing choice
function maps a subsingleton~$K \subseteq M$ to the unique element~$x \in M$
such that~$\nabla(x \in K')$, where~$K' \defeq K \cup \{ 0 \,|\, \text{$K$
inhabited} \Rightarrow \nabla\bot \}$. Since~$K'$ has the property
that~$\nabla(\text{$K$ is a singleton})$, such an element~$x$ exists and is unique
by the sheaf condition.

Now let~$M$ be a module which is separated for some XXX modal operator~$\nabla$.
Then its sheafification is a functionally flabby module into which~$M$ embeds.

Finally, let~$M$ be an arbitrary module. For any element~$x \in M$,
let~$\nabla_x$ be the modal operator with~$\nabla_x\varphi \defeqv ((\varphi \Rightarrow x
= 0) \Rightarrow x = 0)$. The module~$M$ might not be~$\nabla_x$-separated for
a particular element~$x$, but jointly XXX
\end{proof}
